\chapter{Evaluation}\label{ch:evaluation}
Our evaluation answers the following questions.
(i) How well does {\sys} mitigate state-of-the-art network side-channel attacks?
(ii) What are the overheads associated with varying DP relevant configuration parameters?
(iii) What are {\sys}'s overall costs on privacy and bandwidth for different classes of applications?
(iv) How do {\sys}'s privacy guarantees and performance overheads compare to prior techniques?


For our experiments, we use a AMD Ryzen 7 7700X desktop each with eight 4.5 GHz CPUs, 32 GB RAM, 1 TB storage, and a GTX 4090 GPU.
We use two applications for case studies, a video streaming service and a medical web service, which we describe below.
We collect two different sets of traces to evaluate the privacy and overhead of our shaping mechanism.
One dataset of traffic traces collected from a video streaming service, and the other one collected from a medical web service.
\paragraph{Video service.}
The video streaming service is hosted on an Nginx 1.23.4 web server and is used to serve 100 YouTube videos in 720p resolution.
The videos are stored on a standard file system on the host OS and have durations ranging from 5 min to 130.3 min (median 12.6 min) and sizes ranging from 2.7 MB to 1.4 GB (median 73.7 MB).
We stream the first 5 minutes of each video 100 times and collect the traces, leading to 10000 traces in total.

\paragraph{Web service.}
The web service is also hosted on Nginx 1.23.4 and is used to serve a corpus of 100 static HTML pages of a medical website.
The web pages are stored on a standard file system on the host OS and have sizes ranging from 54 KB to 147 KB (median: 90 KB).
Similar to video dataset, we request each webpage 100 times, resulting in a dataset with 10000 traces in total.
%

We design and implement a traffic shaping simulator to evaluate the bandwidth overhead and privacy guarantees of {\sys} differentially private traffic shaping mechanism.
The simulator helps users to configure parameters of {\sys} shaping mechanism, balancing the trade-offs between privacy and overhead according to their requirement.
They can use optimal parameters in the actual {\sys} system, which we design in \Cref{sec:tunnel-design} and implement as part of NetShaper paper {\addref}.
We implemented the simulator and our data-processing pipeline in 4589 lines of Python code.
In this chapter, we first elaborate on the components of our simulator, and the way we implement it. 
Then, we provide a brief overview of our TCN-based Video Identification attack, where we use temporal neural networks (TCN) to map the pattern of the traffic trace to its content. 
In the rest of the chapter, using our simulator and TCN-based attack, we evaluate {\sys}'s privacy and bandwidth overhead trade-offs.

\section{Traffic Shaping Simulator}\label{sec:eval-simulator}
\input{src/evaluation/simulator.tex}

\section{TCN-based Video Identification}\label{sec:eval-tcn}
\input{src/evaluation/TCN.tex}

\section{Empirical Privacy Evaluation}\label{sec:eval-empirical-privacy}
\input{src/evaluation/empirical_privacy.tex}

\section{Impact of Privacy Parameters}\label{sec:eval-privacy-params}
\input{src/evaluation/privacy_parameters.tex}

\section{DP Shaping bandwidth Overhead}\label{sec:eval-bw}
\input{src/evaluation/bandwidth_overhead.tex}