%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

%% https://www.grad.ubc.ca/current-students/dissertation-thesis-preparation/preliminary-pages
%% 
%% LAY SUMMARY Effective May 2017, all theses and dissertations must
%% include a lay summary.  The lay or public summary explains the key
%% goals and contributions of the research/scholarly work in terms that
%% can be understood by the general public. It must not exceed 150
%% words in length.

\chapter{Lay Summary}
Internet applications have long relied on encryption to protect our online security and privacy.
However, encryption cannot protect against a class of attacks called network side-channel attacks.
These attacks use the packet sizes and their timing in the network to infer sensitive information about users.
One way to counter these attacks is through \emph{traffic shaping}, where the packet sizes and timing are modified to hide users' private information from the attacker.
However, balancing between privacy and overhead can be tricky.
To address this challenge, we introduce a novel network side-channel mitigation framework called {\sys}.
It dynamically reshapes users' traffic at regular intervals, ensuring privacy remains intact even over long durations of transmission.
{\sys} allows users to balance the trade-off between privacy, overhead, and latency effectively.
It defeats state-of-the-art traffic analysis attacks.
Furthermore, {\sys} uses differential privacy to provide formal and quantifiable privacy guarantees, protecting users' private information from future, more sophisticated attacks.

