%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Preface}

This thesis contains text and material from the following publication~\cite{netshaper}:
\begin{itemize}
  \item "NetShaper: A Differentially Private Network Side-Channel Mitigation System".
  \\
  Amir Sabzi, Rut Vora, Swati Goswami, Margo Seltzer, Mathias Lécuyer, Aastha Mehta. \textit{Under Review}
\end{itemize}
In greater detail, the subsequent paragraphs elaborate on the origins of the text and material presented in this thesis.
\begin{itemize}
  \item \textbf{\Cref{ch:introduction}}: The introduction is written by me. 
  \item \textbf{\Cref{ch:background}}: Background and Prior work is largely written by me. However, {\sys}'s threat model (\ref{sec:threat-model}) shares content with the NetShaper paper.
  \item \textbf{\Cref{ch:dp-shaping}}: The content of \Cref{ch:dp-shaping} is derived from Section 3 of the NetShaper paper~\cite{netshaper}, which is written by me in collaboration with my advisors, Aastha Mehta and Mathias L\'{e}cuyer. 
  \item \textbf{\Cref{ch:design}}: The content of this chapter partially derived from Section 4 of the NetShaper paper~\cite{netshaper}, which is written by me in collaboration with my advisor, Aastha Mehta. \Cref{sec:tunnel-overview} and \Cref{sec:tunnel-design} are mostly taken from the paper.
  \item \textbf{\Cref{ch:evaluation}}: I conducted all the evaluations presented in the thesis.
  \Cref{sec:eval-simulator} and \Cref{sec:eval-tcn} are written by me. The content of \Cref{sec:eval-empirical-privacy}, \Cref{sec:eval-privacy-params}, and \Cref{sec:eval-comparison-others} are derived from Section 5 of NetShaper paper.
  To create the graphs presented in \Cref{fig:video-latency-vs-dpInt} and \Cref{fig:web-latency-vs-dpInt}, I utilized the NetShaper's artifact developed mainly by Rut Vora in collaboration with me.
 
  \item \textbf{\Cref{ch:related-work} and \Cref{ch:conclusion}}: These two chapters are written by me.




\end{itemize}